\vspace{-12pt}
\section{Experimental Setup}
\vspace{-4pt}


\vspace{-8pt}
\subsection{Datasets}
\vspace{-4pt}

When the original SDR paper was published, only a single collection with results of baseline method implementations was available. 
We intend to assess the generalisability of their SDR method on several new collections which have been released since. The collections we consider are:
%In the five years since the SDR paper was published, several new collections have been made available that we intend to replicate SDR on to assess the methods' generalisability. The collections that we have chosen to replicate SDR on include:

\begin{description}[leftmargin=8pt]
	\item[CLEF TAR 2017~\cite{kanoulas2017clef}] This is the original dataset that was used to study SDR. We include this dataset to confirm that we achieve the same or similar results as the original paper. This collection includes 50 systematic review topics on diagnostic test accuracy -- a type of systematic review that is challenging to create. The 50 topics are split into 20 training topics and 30 testing topics. In our evaluation, we removed topics CD010653, CD010771, CD010386, CD012019, CD011549 as they contained only a single or no relevant studies to use as seed studies. For our experiments using multiple seed studies, we further removed topics CD010860, CD010775, CD010896, CD008643, CD011548, CD010438, CD010633, CD008686 due to low numbers of relevant studies.
	\item[CLEF TAR 2018~\cite{kanoulas2018clef}] This collection adds 30 diagnostic test accuracy systematic reviews as topics to the existing 2017 collection; however, it also removes eight because they are not `reliable for training or testing purposes. In total, this collection contains 72 topics. Our evaluation only used 30 additional reviews of the 2018 dataset and removed topics CD012216, CD009263, CD011515, CD011602, and CD010680 as they contained only a single or no relevant studies to use as seed studies. We also removed topic CD009263 because we ran into memory issues when running experiments on this topic due to many candidate documents (approx. 80,000). For our experiments using multiple seed studies, we removed topics CD012083, CD012009, CD010864, CD011686, CD011420 due to low numbers of relevant studies.
	\item[CLEF TAR 2019~\cite{kanoulas2019clef}] This collection further develops on the previous years' by also including systematic reviews of different types. From this collection, we use the 38 systematic reviews of interventions (i.e., a different type of diagnostic test accuracy).\footnote{Although the overview paper claims there are 40 interventions topics, there are two topics that appear in both training and testing splits. However, like the previous datasets, we ignore these splits and combine the training and testing splits.} We use this collection to study the generalisability of SDR on other kinds of systematic reviews. In our evaluation, we removed topics CD010019, CD012342, CD011140, CD012120, CD012521 as they contained only a single or no relevant studies to use as seed studies. For our experiments using multiple seed studies, we further removed topics CD011380, CD012521, CD009069, CD012164, CD007868, CD005253, CD012455 due to low numbers of relevant studies.
	%\item[SR'17~\cite{scells2017collection}] This collection contains 125 topics of intervention systematic reviews. We also use this collection to investigate the generalisability of SDR on systematic reviews other than diagnostic test accuracy.
\end{description}

\vspace{-22pt}
\subsection{Baselines}
\vspace{-4pt}

The baselines in the original paper included the best performing method from the CLEF TAR 2017 participants, several seed-study-based methods, and variations of the scoring function used by SDR.
%
For our experiments, we compare our reproduction of SDR to all of the original baselines that we have also reproduced from the original paper.%, in addition to the results of others on each of the datasets, where available (i.e., participants to the CLEF TAR shared tasks).
%
The baselines in the original paper include: BM25-\{BOW,BOC\}, QLM-\{BOW,BOC\}, SDR-\{BOW,BOC\}, and AES-\{BOW,BOC\}. The last method, AES, is an embedding-based method that averages the embeddings for all terms in the seed studies. The AES method uses pre-trained word2vec embeddings using PubMed and Wikipedia (as specified in the original paper). We also include a variation that uses only PubMed embeddings (AES-P). Finally, we also include the linear interpolation between SDR and AES, using the same parameter as the original paper ($\alpha=0.3$). We use the same versions of the pre-trained embeddings as the original paper.

\vspace{-12pt}
\subsection{Evaluation Measures}
\vspace{-4pt}

For comparison to the original paper, we use the same evaluation measures. These include MAP, precision@k, recall@k, LastRel\%, and Work Saved over Sampling (WSS). LastRel is a measure introduced at CLEF TAR'17~\cite{kanoulas2017clef}. It is calculated as the rank position of the last relevant document. LastRel\% is the normalised percentage of studies that must be screened in order to obtain all relevant studies. Work Saved Over Sampling; a measure initially proposed to measure classification effectiveness~\cite{cohen2006reducing}, is calculated instead here, by computing the fraction of studies that can be removed from screening to obtain all relevant documents; i.e., $\text{WSS} = \frac{|C|-\text{LastRel}}{|C|}$.
Where $C$ is the number of studies originally retrieved (i.e., the candidate set for re-ranking). 
%
For precision@k and recall@k, we report much deeper levels of $k$: the original paper reported $k=\{10,20,30\}$; where we report $k=\{10,100,1000\}$. Furthermore, we also report nDCG at these k-values, as it provides additional information about relevant study rank positions.
%
We compute LastRel\% and WSS using the scripts used in CLEF TAR 2017. For all other evaluation measures we use \texttt{trec\_eval} (version 9.0.7).

\vspace{-12pt}
\subsection{Document Pre-Processing}
\vspace{-4pt}
It is widely known that document pre-processing (e.g., tokenisation, stopwords, or stemming) can have a profound effect on ranking performance~\cite{croft2002combining}. Although the original paper provides information about the versions of the libraries it uses for ranking, there were fewer details, such as how documents were tokenised or which stopword list was used. We reached out to the original authors to confirm the exact experimental settings. From the original paper, documents were split using space, then stopwords were removed using nltk.

The modifications we made to the document pre-processing pipeline were that documents were first pre-processed to remove punctuation marks and then tokenised using gensim version 3.2.0 tokeniser. For stopwords, as the original authors have not specified the nltk version, we used the latest version at the time of publishing, version 3.6.3. Then terms used are lowercased for in all methods except for AES. No stemming has been applied in either pre-processing pipeline.

\vspace{-8pt}