
\section{Result}


\subsection{RQ1: Impact of Segmentation Strategies in In-Corpus Retrieval}

To establish baseline effectiveness characteristics of different segmentation strategies in realistic in-corpus retrieval scenarios, we evaluated six segmentation methods across six BEIR datasets using four embedding models under the pre-embedding chunking paradigm. This research question addresses the core practical concern: which segmentation approach performs best when retrieval occurs across a corpus of documents?

\textbf{No single chunking strategy dominates across all embedding models and datasets.} Across the six in-corpus retrieval tasks, paragraph-based chunking achieves the highest average nDCG@10 for three of the four embedding models (Jina-v2: 0.4303, Jina-v3: 0.4948, E5-base: 0.4997), while fixed-size chunking performs best with Nomic embeddings (0.4828). This variability suggests that the optimal segmentation strategy is contingent on how different embedding models encode semantic boundaries and the inherent structure of the target domain.

\textbf{Semantically-informed and LLM-guided strategies underperform relative to their computational cost.} Contrary to expectations that more sophisticated semantic analysis would improve retrieval effectiveness, advanced methods consistently underperform simpler heuristics. Proposition-based chunking yields the lowest average nDCG@10 across all models (ranging from 0.3487 to 0.3916), representing a 15--20\% performance degradation compared to paragraph-based chunking. LumberChunker ranks fourth or fifth in average corpus effectiveness across datasets. For instance, with Jina-v3, paragraph chunking outperforms LumberChunker by 11\% (0.4948 vs 0.4463) and proposition-based chunking by 26\% (0.4948 vs 0.3916). Given the significantly higher computational cost of LLM-based methods, these results suggest that the added complexity does not translate to retrieval gains in multi-document settings.

\textbf{Dataset characteristics and domain-specific structure influence segmentation effectiveness.} The relative performance of segmentation methods varies meaningfully across different corpus types. For domain-specific datasets like SciFact and TREC-COVID, sentence-based chunking often performs competitively or best (e.g., SciFact with Jina-v2: 0.6548; TREC-COVID with Nomic: 0.7859), suggesting that shorter, semantically-bounded units work well when documents have highly specialized terminology and structure. In contrast, for argumentative text (ArguAna), paragraph and fixed-size chunking consistently outperform more sophisticated strategies, indicating that natural discourse boundaries are crucial for certain document types. This pattern suggests that segmentation strategy selection should account for the structural characteristics of the target corpus.

\textbf{Embedding model architecture affects sensitivity to segmentation choice.} The variance in effectiveness across segmentation methods differs substantially between embedding models, indicating that not all models are equally robust to suboptimal chunk boundaries. Jina-v2 exhibits the highest sensitivity with a 23\% effectiveness gap between best and worst strategies (0.4303 vs 0.3487), while E5-base demonstrates greater robustness with only an 11\% gap (0.4997 vs 0.3883). This finding suggests that some embedding models are inherently better equipped to handle suboptimal segmentation, which is an important consideration when deploying retrieval systems.

\textbf{Overall, structure-based heuristics provide the most reliable and practical approach for in-corpus retrieval.} Paragraph-based chunking emerges as the most robust general-purpose strategy, achieving the highest average nDCG@10 in three of four models and consistently ranking in the top-2 across individual datasets. Fixed-size chunking offers comparable effectiveness (within 2\% of paragraph chunking on average) with the added computational advantage of deterministic and parallelizable processing. Surprisingly, despite their conceptual sophistication, LLM-guided strategies provide diminishing returns: proposition-level chunking averages 15--20\% lower effectiveness than paragraph chunking across all models, while incurring substantially higher computational costs. These results directly address RQ1 by demonstrating that for standard in-corpus retrieval, simpler segmentation methods that either respect natural document structure or maintain consistency provide superior effectiveness and robustness compared to semantic-aware alternatives, and do so with significantly lower computational overhead.



\begin{table}[htbp]
	\centering
		\caption{Effectiveness comparison across different models, chunking strategies, and datasets using DCG@10 for GutenQA and nDCG@10 for other datasets (regular encoder)}
	\label{tab:results_regular_encoder}
	\begin{tabular}{llcccccccc}
		\toprule
		&  & \multicolumn{1}{c}{\textbf{\textit{document}}} & \multicolumn{7}{c}{\textbf{\textit{corpus}}} \\
		\cmidrule(lr){3-3} \cmidrule(lr){4-10}
		&  & GutenQA & fiqa & nfcorpus & scifact & trec-covid & arguana & scidocs & Avg \\
		\midrule
		\multirow{6}{*}{\rotatebox{90}{\textbf{Jina-v2}}} & Paragraph & 0.3893 & \textbf{0.3347} & \textbf{0.3042} & 0.6389 & 0.6518 & 0.4682 & 0.1843 & \textbf{0.4303} \\
		& Sentence & 0.3261 & 0.3096 & 0.2847 & \textbf{0.6548} & \textbf{0.6674} & 0.4675 & 0.1732 & 0.4262 \\
		& Fixed-Size & 0.3889 & 0.3339 & 0.2604 & 0.6350 & 0.6437 & \textbf{0.4706} & \textbf{0.1853} & 0.4215 \\
		& Semantic & 0.3858 & 0.3030 & 0.2746 & 0.6445 & 0.6618 & 0.4022 & 0.1760 & 0.4104 \\
		& Lumber & 0.4782 & 0.2754 & 0.2887 & 0.6540 & 0.6456 & 0.3906 & 0.1721 & 0.4044 \\
		& Proposition & \textbf{0.5556} & 0.2186 & 0.2995 & 0.6331 & 0.4292 & 0.3681 & 0.1436 & 0.3487 \\
		& \textbf{Avg} & 0.4207 & 0.2959 & 0.2854 & 0.6434 & 0.6166 & 0.4279 & 0.1724 & 0.4069 \\
		\midrule
		\multirow{6}{*}{\rotatebox{90}{\textbf{Jina-v3}}} & Paragraph & 0.4574 & \textbf{0.4747} & \textbf{0.3663} & 0.7247 & \textbf{0.7721} & \textbf{0.4327} & 0.1984 & \textbf{0.4948} \\
		& Sentence & 0.3877 & 0.4333 & 0.3566 & 0.7163 & 0.7135 & 0.4256 & 0.1888 & 0.4723 \\
		& Fixed-Size & 0.4827 & 0.4728 & 0.3596 & \textbf{0.7262} & 0.7557 & 0.4325 & \textbf{0.1985} & 0.4909 \\
		& Semantic & 0.4105 & 0.4396 & 0.3596 & 0.7103 & 0.7474 & 0.3894 & 0.1890 & 0.4726 \\
		& Lumber & \textbf{0.5693} & 0.4028 & 0.3534 & 0.6845 & 0.6900 & 0.3671 & 0.1797 & 0.4463 \\
		& Proposition & 0.5484 & 0.2858 & 0.3579 & 0.6690 & 0.5756 & 0.3044 & 0.1569 & 0.3916 \\
		& \textbf{Avg} & 0.4760 & 0.4182 & 0.3589 & 0.7052 & 0.7091 & 0.3920 & 0.1852 & 0.4614 \\
		\midrule
		\multirow{6}{*}{\rotatebox{90}{\textbf{Nomic}}} & Paragraph & 0.4893 & 0.3802 & 0.3509 & 0.7047 & 0.7652 & 0.4904 & 0.1808 & 0.4787 \\
		& Sentence & 0.4146 & 0.3620 & 0.3502 & \textbf{0.7150} & 0.7472 & \textbf{0.5084} & 0.1732 & 0.4760 \\
		& Fixed-Size & 0.5104 & \textbf{0.3839} & 0.3492 & 0.7050 & \textbf{0.7859} & 0.4915 & \textbf{0.1812} & \textbf{0.4828} \\
		& Semantic & 0.4274 & 0.3562 & 0.3506 & 0.7040 & 0.7431 & 0.4434 & 0.1707 & 0.4613 \\
		& Lumber & \textbf{0.6048} & 0.3347 & \textbf{0.3513} & 0.7093 & 0.7193 & 0.4315 & 0.1673 & 0.4522 \\
		& Proposition & 0.5827 & 0.2575 & 0.3358 & 0.6853 & 0.5580 & 0.3693 & 0.1441 & 0.3916 \\
		& \textbf{Avg} & 0.5049 & 0.3457 & 0.3480 & 0.7039 & 0.7198 & 0.4557 & 0.1696 & 0.4571 \\
		\midrule
		\multirow{6}{*}{\rotatebox{90}{\textbf{E5-Large}}} & Paragraph & 0.4663 & \textbf{0.4617} & 0.3566 & \textbf{0.7129} & 0.6634 & \textbf{0.5999} & 0.2038 & \textbf{0.4997} \\
		& Sentence & 0.4063 & 0.4315 & 0.3583 & 0.6873 & 0.6712 & 0.5646 & 0.1836 & 0.4828 \\
		& Fixed-Size & 0.4862 & 0.4599 & 0.3495 & 0.7078 & 0.6590 & 0.5987 & \textbf{0.2058} & 0.4968 \\
		& Semantic & 0.3186 & 0.4173 & 0.3583 & 0.6892 & 0.6784 & 0.5540 & 0.1888 & 0.4810 \\
		& Lumber & 0.5234 & 0.3739 & 0.3531 & 0.6748 & \textbf{0.6931} & 0.5233 & 0.1792 & 0.4663 \\
		& Proposition & \textbf{0.5530} & 0.2522 & \textbf{0.3602} & 0.6851 & 0.5611 & 0.3163 & 0.1551 & 0.3883 \\
		& \textbf{Avg} & 0.4590 & 0.3994 & 0.3560 & 0.6928 & 0.6544 & 0.5261 & 0.1861 & 0.4691 \\
		\bottomrule
	\end{tabular}
\end{table}



\subsection{RQ2: Do Segmentation Strategies Generalize Across Retrieval Paradigms?}

To determine whether the effectiveness rankings observed in in-corpus retrieval generalize to in-document retrieval, we evaluated all six segmentation methods on the GutenQA dataset using the same four embedding models under both pre-embedding and contextualized chunking paradigms. This research question tests whether segmentation strategy preferences are fundamental or paradigm-dependent.

\textbf{Segmentation effectiveness rankings show dramatic inversion between retrieval paradigms.} Contrary to in-corpus retrieval results, methods that excel on BEIR fall short on GutenQA, while those underperforming on multi-document tasks rank highly on single-document retrieval. Proposition-based chunking delivers the highest GutenQA DCG@10 scores for three of the four embedding models (e.g., 0.5556 with Jina-v2 and 0.5530 with E5-base), yet it yields the lowest average nDCG@10 on BEIR in every case, trailing paragraph chunking by 18\% for Jina-v2 (0.3487 vs.\ 0.4303) and 22\% for E5-base (0.3883 vs.\ 0.4997). Similarly, LumberChunker leads the GutenQA rankings for Jina-v3 (0.5693 DCG@10) but drops to fourth place on BEIR with 0.4463 average nDCG@10. In sharp contrast, simple heuristics such as paragraph and fixed-size chunking rarely achieve top scores on GutenQA but consistently occupy the top two ranks across all BEIR datasets. This dramatic reversal indicates that retrieval paradigm fundamentally changes which segmentation strategies are effective.

\textbf{Paradigm-specific optimization creates poor transferability.} The inversion of effectiveness rankings demonstrates that chunking strategies optimized for precise passage localization within single documents do not generalize to open-domain multi-document retrieval. Proposition-based chunking's strength lies in creating highly specific, semantically-bounded chunks that facilitate exact fact localization. However, this same specificity becomes a liability in in-corpus retrieval, where the retriever must first identify relevant documents among thousands of candidates. Conversely, coarser structural boundaries preserve semantic context needed for broad relevance matching across a corpus, even though they sacrifice some in-document precision.

\textbf{No universal segmentation strategy satisfies both retrieval paradigms.} The lack of a method performing strongly across both settings definitively answers RQ2: segmentation strategy effectiveness is paradigm-dependent, not fundamental. This finding has critical implications for practitioners deploying retrieval systems: a single chunking configuration cannot effectively serve both in-corpus and in-document retrieval tasks. Systems requiring both capabilities must either maintain separate chunking pipelines or accept suboptimal performance on one retrieval paradigm.





\begin{table}[htbp]
	\centering
	\caption{Effectiveness comparison across different models, chunking strategies, and datasets using DCG@10 for GutenQA and nDCG@10 for other datasets (late encoder)}
	\label{tab:results_late_encoder}
	\begin{tabular}{llcccccccc}
		\toprule
		&  & \multicolumn{1}{c}{\textbf{\textit{document}}} & \multicolumn{7}{c}{\textbf{\textit{corpus}}} \\
		\cmidrule(lr){3-3} \cmidrule(lr){4-10}
		&  & GutenQA & fiqa & nfcorpus & scifact & trec-covid & arguana & scidocs & Avg \\
		\midrule
		\multirow{6}{*}{\rotatebox{90}{\textbf{Jina-v2}}} & Paragraph & 0.3476 & 0.3346 & 0.3041 & 0.6397 & 0.6618 & 0.4666 & 0.1854 & 0.4320 \\
		& Sentence & 0.3084 & \textbf{0.3392} & 0.3033 & 0.6583 & \textbf{0.6791} & 0.4764 & 0.1839 & \textbf{0.4400} \\
		& Fixed-Size & 0.3799 & 0.3351 & 0.3003 & 0.6448 & 0.6649 & 0.4685 & \textbf{0.1858} & 0.4332 \\
		& Semantic & 0.4041 & 0.2195 & 0.2900 & 0.6489 & 0.6076 & 0.4715 & 0.1836 & 0.4035 \\
		& Lumber & 0.4290 & 0.2223 & 0.3079 & 0.6527 & 0.6516 & 0.4759 & 0.1855 & 0.4160 \\
		& Proposition & \textbf{0.5280} & 0.3042 & \textbf{0.3210} & \textbf{0.6632} & 0.4884 & \textbf{0.4869} & 0.1655 & 0.4049 \\
		& \textbf{Avg} & 0.3995 & 0.2925 & 0.3044 & 0.6513 & 0.6256 & 0.4743 & 0.1816 & 0.4216 \\
		\midrule
		\multirow{6}{*}{\rotatebox{90}{\textbf{Jina-v3}}} & Paragraph & 0.2816 & 0.4306 & 0.3442 & 0.6826 & 0.6921 & \textbf{0.4732} & 0.2034 & 0.4710 \\
		& Sentence & 0.2524 & \textbf{0.4355} & 0.3443 & 0.6841 & \textbf{0.7046} & 0.4605 & 0.2011 & \textbf{0.4717} \\
		& Fixed-Size & 0.3411 & 0.4308 & 0.3442 & 0.6856 & 0.6881 & 0.4732 & \textbf{0.2036} & 0.4709 \\
		& Semantic & 0.3356 & 0.2895 & 0.3474 & 0.6880 & 0.6527 & 0.4729 & 0.2019 & 0.4421 \\
		& Lumber & 0.3789 & 0.2857 & 0.3506 & \textbf{0.6947} & 0.6826 & 0.4691 & 0.2020 & 0.4474 \\
		& Proposition & \textbf{0.4984} & 0.3670 & \textbf{0.3551} & 0.6937 & 0.5229 & 0.4328 & 0.1883 & 0.4266 \\
		& \textbf{Avg} & 0.3480 & 0.3732 & 0.3476 & 0.6881 & 0.6571 & 0.4636 & 0.2001 & 0.4550 \\
		\midrule
		\multirow{6}{*}{\rotatebox{90}{\textbf{Nomic}}} & Paragraph & 0.1839 & \textbf{0.3801} & 0.3508 & 0.7057 & 0.7361 & 0.4936 & \textbf{0.1808} & 0.4745 \\
		& Sentence & 0.1557 & 0.3777 & 0.3536 & 0.7129 & \textbf{0.7517} & 0.4883 & 0.1778 & \textbf{0.4770} \\
		& Fixed-Size & 0.2127 & 0.3796 & 0.3515 & 0.7058 & 0.7316 & \textbf{0.4941} & 0.1806 & 0.4738 \\
		& Semantic & 0.2435 & 0.2804 & 0.3535 & 0.7036 & 0.7052 & 0.4890 & 0.1786 & 0.4517 \\
		& Lumber & 0.2395 & 0.2757 & \textbf{0.3604} & \textbf{0.7191} & 0.6790 & 0.4823 & 0.1796 & 0.4494 \\
		& Proposition & \textbf{0.4213} & 0.3145 & 0.3515 & 0.7124 & 0.4502 & 0.4773 & 0.1530 & 0.4098 \\
		& \textbf{Avg} & 0.2428 & 0.3347 & 0.3535 & 0.7099 & 0.6756 & 0.4874 & 0.1751 & 0.4560 \\
		\midrule
		\multirow{6}{*}{\rotatebox{90}{\textbf{E5-Large}}} & Paragraph & 0.4223 & \textbf{0.4613} & \textbf{0.3576} & \textbf{0.7152} & \textbf{0.6630} & \textbf{0.5994} & \textbf{0.2064} & \textbf{0.5005} \\
		& Sentence & 0.3621 & 0.4608 & 0.3553 & 0.7030 & 0.6479 & 0.5945 & 0.2061 & 0.4946 \\
		& Fixed-Size & 0.4863 & 0.4601 & 0.3510 & 0.7095 & 0.6615 & 0.5978 & 0.2063 & 0.4977 \\
		& Semantic & 0.3259 & 0.3227 & 0.3549 & 0.7006 & 0.6430 & 0.5923 & 0.2055 & 0.4698 \\
		& Lumber & \textbf{0.5245} & 0.3015 & 0.3518 & 0.6976 & 0.6137 & 0.5922 & 0.2050 & 0.4603 \\
		& Proposition & 0.5117 & 0.3306 & 0.3405 & 0.6427 & 0.4160 & 0.5056 & 0.1826 & 0.4030 \\
		& \textbf{Avg} & 0.4388 & 0.3895 & 0.3518 & 0.6948 & 0.6075 & 0.5803 & 0.2020 & 0.4710 \\
		\bottomrule
	\end{tabular}
\end{table}




\subsection{RQ3: Effectiveness of Contextualized Chunking}

To assess whether contextualized chunking (late encoding) provides consistent improvements across segmentation methods and retrieval tasks, we compared late encoding to pre-embedding approaches for all six segmentation strategies across both in-corpus (BEIR) and in-document (GutenQA) retrieval settings. This research question evaluates whether contextualized chunking is a universal improvement or highly dependent on specific configurations.

\textbf{Contextualized chunking provides significant but highly method-dependent gains on in-corpus retrieval.} Proposition-based chunking experiences dramatic improvements across BEIR datasets when paired with late encoding, gaining +18.74\% on average for Jina-v2, +14.06\% for Jina-v3, +7.82\% for Nomic, and +11.87\% for E5-base. These gains are particularly pronounced on challenging domains (e.g., +39.17\% on FiQA with Jina-v2, +42.20\% on ArguAna with Jina-v3, +59.84\% on ArguAna with E5-base). In contrast, simple heuristics like paragraph and fixed-size chunking remain largely stable on BEIR, with average changes within $\pm$0.5\% across most embedding models. This dichotomy reveals that contextualized embeddings selectively benefit semantically-structured chunks while providing minimal benefit to structurally-simple ones.

\textbf{Contextualized chunking severely degrades performance on in-document retrieval across all methods.} While LLM-guided methods gain substantially on in-corpus tasks, every segmentation strategy experiences severe performance loss on GutenQA when switched to late encoding. Paragraph chunking suffers the most extreme degradation ($-$62.41\% DCG@10 with Nomic, $-$38.43\% with Jina-v3, $-$10.72\% with Jina-v2), indicating that full-document context actively harms passage-level precision. Even proposition-based chunking, which thrives on BEIR with contextualization, still loses performance on GutenQA ($-$27.70\% with Nomic, $-$9.12\% with Jina-v3). This universal degradation on in-document retrieval demonstrates a fundamental incompatibility between contextualized embeddings and fine-grained information localization tasks.

\textbf{Contextualized chunking effectiveness is highly contingent on both chunking strategy and dataset domain.} Beyond the in-corpus versus in-document distinction, contextualized chunking's impact varies dramatically by dataset type. Proposition-based chunking achieves its largest gains on argumentative corpora (ArguAna: +32.26\% for Jina-v2, +42.20\% for Jina-v3, +29.26\% for Nomic, +59.84\% for E5-base) but suffers regressions on structured scientific datasets (TREC-COVID: $-$9.16\% for Jina-v3, $-$25.85\% for E5-base). LumberChunker similarly exhibits domain-specific swings, gaining +27.78\% on ArguAna with Jina-v3 yet losing $-$29.08\% on FiQA. These patterns suggest that contextualized embeddings are most effective when documents contain complex argumentative structures requiring global context, but provide diminishing returns or cause harm on well-structured technical content.

\textbf{Contextualized chunking is not universally beneficial; its value depends on matching method to task.} Overall, contextualized chunking delivers modest average improvements across BEIR (ranging from +0.84\% to +4.75\% depending on embedding model) but at severe cost to in-document retrieval performance (averaging $-$52.39\% loss for Nomic, $-$27.25\% for Jina-v3, $-$4.83\% for Jina-v2, $-$4.22\% for E5-base). These results directly answer RQ3: contextualized chunking is not a universal upgrade but rather a method-specific tool. LLM-guided strategies like proposition-based chunking unlock their full potential when paired with contextualized embeddings on in-corpus tasks, while structural heuristics derive minimal benefit. Critically, any system supporting both in-corpus and in-document retrieval cannot use contextualized chunking without accepting substantial performance degradation on one paradigm. Practitioners must make an explicit trade-off: preserve in-document retrieval performance with pre-embedding approaches, or sacrifice document-level precision to maximize corpus-level retrieval gains for LLM-guided methods.




\begin{table}[htbp]
	\centering
	\definecolor{lightgreen}{RGB}{220,255,220}
	\definecolor{lightred}{RGB}{255,220,220}
	\caption{Late-encoder effectiveness relative to the regular encoder (baseline). Values show percentage change (light green=improvement, light red=degradation)}
	\label{tab:encoder_comparison}
	\begin{tabular}{llcccccccc}
		\toprule
		&  & \multicolumn{1}{c}{\textbf{\textit{document}}} & \multicolumn{7}{c}{\textbf{\textit{corpus}}} \\
		\cmidrule(lr){3-3} \cmidrule(lr){4-10}
		&  & GutenQA & fiqa & nfcorpus & scifact & trec-covid & arguana & scidocs & Avg \\
		\midrule
		\multirow{6}{*}{\textbf{Jina-v2}} & Paragraph & \cellcolor{lightred}-10.72 & \cellcolor{lightred}-0.02 & \cellcolor{lightred}-0.03 & \cellcolor{lightgreen}+0.12 & \cellcolor{lightgreen}+1.53 & \cellcolor{lightred}-0.33 & \cellcolor{lightgreen}+0.61 & \cellcolor{lightgreen}+0.31 \\
		& Sentence & \cellcolor{lightred}-5.43 & \cellcolor{lightgreen}+9.57 & \cellcolor{lightgreen}+6.52 & \cellcolor{lightgreen}+0.52 & \cellcolor{lightgreen}+1.76 & \cellcolor{lightgreen}+1.89 & \cellcolor{lightgreen}+6.17 & \cellcolor{lightgreen}+4.40 \\
		& Fixed-Size & \cellcolor{lightred}-2.32 & \cellcolor{lightgreen}+0.35 & \cellcolor{lightgreen}\textbf{+15.32} & \cellcolor{lightgreen}+1.55 & \cellcolor{lightgreen}+3.30 & \cellcolor{lightred}-0.44 & \cellcolor{lightgreen}+0.27 & \cellcolor{lightgreen}+3.39 \\
		& Semantic & \cellcolor{lightgreen}\textbf{+4.75} & \cellcolor{lightred}-27.57 & \cellcolor{lightgreen}+5.59 & \cellcolor{lightgreen}+0.69 & \cellcolor{lightred}-8.19 & \cellcolor{lightgreen}+17.22 & \cellcolor{lightgreen}+4.31 & \cellcolor{lightred}-1.32 \\
		& Lumber & \cellcolor{lightred}-10.30 & \cellcolor{lightred}-19.29 & \cellcolor{lightgreen}+6.66 & \cellcolor{lightred}-0.19 & \cellcolor{lightgreen}+0.93 & \cellcolor{lightgreen}+21.85 & \cellcolor{lightgreen}+7.80 & \cellcolor{lightgreen}+2.96 \\
		& Proposition & \cellcolor{lightred}-4.98 & \cellcolor{lightgreen}\textbf{+39.17} & \cellcolor{lightgreen}+7.18 & \cellcolor{lightgreen}\textbf{+4.75} & \cellcolor{lightgreen}\textbf{+13.79} & \cellcolor{lightgreen}\textbf{+32.26} & \cellcolor{lightgreen}\textbf{+15.29} & \cellcolor{lightgreen}\textbf{+18.74} \\
		& \textbf{Avg} & \cellcolor{lightred}-4.83 & \cellcolor{lightgreen}+0.37 & \cellcolor{lightgreen}+6.87 & \cellcolor{lightgreen}+1.24 & \cellcolor{lightgreen}+2.19 & \cellcolor{lightgreen}+12.07 & \cellcolor{lightgreen}+5.74 & \cellcolor{lightgreen}+4.75 \\
		\midrule
		\multirow{6}{*}{\textbf{Jina-v3}} & Paragraph & \cellcolor{lightred}-38.43 & \cellcolor{lightred}-9.28 & \cellcolor{lightred}-6.02 & \cellcolor{lightred}-5.81 & \cellcolor{lightred}-10.37 & \cellcolor{lightgreen}+9.37 & \cellcolor{lightgreen}+2.52 & \cellcolor{lightred}-3.27 \\
		& Sentence & \cellcolor{lightred}-34.89 & \cellcolor{lightgreen}+0.51 & \cellcolor{lightred}-3.43 & \cellcolor{lightred}-4.49 & \cellcolor{lightred}-1.25 & \cellcolor{lightgreen}+8.20 & \cellcolor{lightgreen}+6.55 & \cellcolor{lightgreen}+1.01 \\
		& Fixed-Size & \cellcolor{lightred}-29.35 & \cellcolor{lightred}-8.88 & \cellcolor{lightred}-4.27 & \cellcolor{lightred}-5.58 & \cellcolor{lightred}-8.95 & \cellcolor{lightgreen}+9.40 & \cellcolor{lightgreen}+2.57 & \cellcolor{lightred}-2.62 \\
		& Semantic & \cellcolor{lightred}-18.24 & \cellcolor{lightred}-34.15 & \cellcolor{lightred}-3.41 & \cellcolor{lightred}-3.14 & \cellcolor{lightred}-12.67 & \cellcolor{lightgreen}+21.43 & \cellcolor{lightgreen}+6.85 & \cellcolor{lightred}-4.18 \\
		& Lumber & \cellcolor{lightred}-33.46 & \cellcolor{lightred}-29.08 & \cellcolor{lightred}-0.78 & \cellcolor{lightgreen}+1.48 & \cellcolor{lightred}-1.08 & \cellcolor{lightgreen}+27.78 & \cellcolor{lightgreen}+12.40 & \cellcolor{lightgreen}+1.79 \\
		& Proposition & \cellcolor{lightred}-9.12 & \cellcolor{lightgreen}\textbf{+28.41} & \cellcolor{lightred}-0.78 & \cellcolor{lightgreen}\textbf{+3.70} & \cellcolor{lightred}-9.16 & \cellcolor{lightgreen}\textbf{+42.20} & \cellcolor{lightgreen}\textbf{+20.01} & \cellcolor{lightgreen}\textbf{+14.06} \\
		& \textbf{Avg} & \cellcolor{lightred}-27.25 & \cellcolor{lightred}-8.75 & \cellcolor{lightred}-3.11 & \cellcolor{lightred}-2.31 & \cellcolor{lightred}-7.25 & \cellcolor{lightgreen}+19.73 & \cellcolor{lightgreen}+8.48 & \cellcolor{lightgreen}+1.13 \\
		\midrule
		\multirow{6}{*}{\textbf{Nomic}} & Paragraph & \cellcolor{lightred}-62.41 & \cellcolor{lightred}-0.03 & \cellcolor{lightred}-0.03 & \cellcolor{lightgreen}+0.14 & \cellcolor{lightred}-3.80 & \cellcolor{lightgreen}+0.65 & \cellcolor{lightgreen}+0.02 & \cellcolor{lightred}-0.51 \\
		& Sentence & \cellcolor{lightred}-62.46 & \cellcolor{lightgreen}+4.33 & \cellcolor{lightgreen}+0.98 & \cellcolor{lightred}-0.28 & \cellcolor{lightgreen}\textbf{+0.60} & \cellcolor{lightred}-3.96 & \cellcolor{lightgreen}+2.66 & \cellcolor{lightgreen}+0.72 \\
		& Fixed-Size & \cellcolor{lightred}-58.33 & \cellcolor{lightred}-1.10 & \cellcolor{lightgreen}+0.63 & \cellcolor{lightgreen}+0.11 & \cellcolor{lightred}-6.91 & \cellcolor{lightgreen}+0.51 & \cellcolor{lightred}-0.36 & \cellcolor{lightred}-1.19 \\
		& Semantic & \cellcolor{lightred}-43.04 & \cellcolor{lightred}-21.28 & \cellcolor{lightgreen}+0.82 & \cellcolor{lightred}-0.04 & \cellcolor{lightred}-5.09 & \cellcolor{lightgreen}+10.29 & \cellcolor{lightgreen}+4.62 & \cellcolor{lightred}-1.78 \\
		& Lumber & \cellcolor{lightred}-60.40 & \cellcolor{lightred}-17.64 & \cellcolor{lightgreen}+2.61 & \cellcolor{lightgreen}+1.39 & \cellcolor{lightred}-5.59 & \cellcolor{lightgreen}+11.78 & \cellcolor{lightgreen}\textbf{+7.35} & \cellcolor{lightred}-0.02 \\
		& Proposition & \cellcolor{lightred}-27.70 & \cellcolor{lightgreen}\textbf{+22.15} & \cellcolor{lightgreen}\textbf{+4.68} & \cellcolor{lightgreen}\textbf{+3.95} & \cellcolor{lightred}-19.32 & \cellcolor{lightgreen}\textbf{+29.26} & \cellcolor{lightgreen}+6.22 & \cellcolor{lightgreen}\textbf{+7.82} \\
		& \textbf{Avg} & \cellcolor{lightred}-52.39 & \cellcolor{lightred}-2.26 & \cellcolor{lightgreen}+1.62 & \cellcolor{lightgreen}+0.88 & \cellcolor{lightred}-6.69 & \cellcolor{lightgreen}+8.09 & \cellcolor{lightgreen}+3.42 & \cellcolor{lightgreen}+0.84 \\
		\midrule
		\multirow{6}{*}{\textbf{E5-Large}} & Paragraph & \cellcolor{lightred}-9.43 & \cellcolor{lightred}-0.09 & \cellcolor{lightgreen}+0.27 & \cellcolor{lightgreen}+0.32 & \cellcolor{lightred}-0.05 & \cellcolor{lightred}-0.08 & \cellcolor{lightgreen}+1.27 & \cellcolor{lightgreen}+0.27 \\
		& Sentence & \cellcolor{lightred}-10.89 & \cellcolor{lightgreen}+6.80 & \cellcolor{lightred}-0.84 & \cellcolor{lightgreen}+2.29 & \cellcolor{lightred}-3.48 & \cellcolor{lightgreen}+5.29 & \cellcolor{lightgreen}+12.28 & \cellcolor{lightgreen}+3.72 \\
		& Fixed-Size & \cellcolor{lightgreen}+0.01 & \cellcolor{lightgreen}+0.05 & \cellcolor{lightgreen}\textbf{+0.42} & \cellcolor{lightgreen}+0.25 & \cellcolor{lightgreen}\textbf{+0.38} & \cellcolor{lightred}-0.14 & \cellcolor{lightgreen}+0.25 & \cellcolor{lightgreen}+0.20 \\
		& Semantic & \cellcolor{lightgreen}\textbf{+2.29} & \cellcolor{lightred}-22.66 & \cellcolor{lightred}-0.96 & \cellcolor{lightgreen}+1.66 & \cellcolor{lightred}-5.22 & \cellcolor{lightgreen}+6.92 & \cellcolor{lightgreen}+8.83 & \cellcolor{lightred}-1.90 \\
		& Lumber & \cellcolor{lightgreen}+0.20 & \cellcolor{lightred}-19.37 & \cellcolor{lightred}-0.39 & \cellcolor{lightgreen}\textbf{+3.37} & \cellcolor{lightred}-11.46 & \cellcolor{lightgreen}+13.18 & \cellcolor{lightgreen}+14.38 & \cellcolor{lightred}-0.05 \\
		& Proposition & \cellcolor{lightred}-7.47 & \cellcolor{lightgreen}\textbf{+31.09} & \cellcolor{lightred}-5.47 & \cellcolor{lightred}-6.18 & \cellcolor{lightred}-25.85 & \cellcolor{lightgreen}\textbf{+59.84} & \cellcolor{lightgreen}\textbf{+17.77} & \cellcolor{lightgreen}\textbf{+11.87} \\
		& \textbf{Avg} & \cellcolor{lightred}-4.22 & \cellcolor{lightred}-0.69 & \cellcolor{lightred}-1.16 & \cellcolor{lightgreen}+0.28 & \cellcolor{lightred}-7.61 & \cellcolor{lightgreen}+14.17 & \cellcolor{lightgreen}+9.13 & \cellcolor{lightgreen}+2.35 \\
		\bottomrule
	\end{tabular}
\end{table}




\section{RQ4: Other Factors}
